### 2022-09-15 chapters/programming_languages/programming_languages.tex
refactoring and fix missing refrences
refactoring
Proofreading

\chapter{Energy Footprint of Programming Languages}
\label{chapter:porgramming_langauges}
In this chapter, we study how the programming language affects the energy the software consumes.
We suggest starting with general micro-benchmarking and watching how each programming language performs with the CPU and memory.
The main goal of this chapter is to advise developers on how to choose a programming language based on their project's needs in order to make their product use the least amount of energy possible.
For such a question, no answer is obvious.
Nonetheless, there are some features we can take from each programming language, such as: 
\begin{itemize}
    \item performance,
    \item community support,
    \item scalability,
    \item energy consumption,
    \item memory usage.
\end{itemize}

@@

\section{Investigating Remote Procedure Call Frameworks}
\import{\currfiledir/rpc}{rpc}

@@

>>>>

\chapter{The Energy Footprint of Programming Frameworks}
\label{chapter:porgramming_langauges}
\section{Introduction}
In this chapter, we study how the programming framework affects the energy the software consumes.
We suggest starting with general micro-benchmarking and watching how each programming framework performs with the CPU and memory.
The main goal of this chapter is to advise developers on how to choose a programming framework based on their project's needs to make their product use the least amount of energy possible.
For such a question, no answer is obvious.
Nonetheless, there are some features we can take from each programming framework, such as:
\begin{itemize}
    \item performance,
    \item community support,
    \item scalability,
    \item energy consumption,
    \item memory usage.
\end{itemize}

@@

\section{Investigating Remote Procedure Call Frameworks}
\import{\currfiledir/rpc}{rpc}
\clearpage

@@

\section{Conclusion\note{missing}}
